Enforced Invariant Confluence

### 2018-04-18 doc/paper/sections/introduction.tex
Work on related work.

\section{Introduction}
When an application designer decides to replicate a piece of data, they have to
make a fundamental choice between weak and strong consistency. Replicating the
data with strong consistency using a technique like state machine
replication~\cite{schneider1990implementing, lamport1998part,
liskov2012viewstamped, ongaro2014search} makes the application designer's life
very easy. To the application developer, a strongly consistent system behaves
exactly like a single-threaded system running on a single node, so reasoning
about the behavior of the system is simple. Unfortunately, strong consistency
is at odds with performance. The CAP theorem and PACELC theorem tell us that
strongly consistent systems suffer from higher latency at best and
unavailability at worst~\cite{brewer2012cap, abadi2012consistency}. On the
other hand, weak consistency models like eventual~\cite{vogels2009eventually},
PRAM~\cite{lipton1988pram}, and causal~\cite{ahamad1995causal} consistency
allow data to be replicated with high availability and low latency, but they
put a tremendous burden on the application designer to reason about the complex
interleavings of operations that are allowed by these weak consistency models.
In fact, weak consistency models strip an application developer of one of the
earliest and most effective tools that is used to reason about the execution of
programs: application invariants~\cite{hoare1969axiomatic}. Even if every
transaction executing in a weakly consistent system individually maintains an
application invariant, the system as a whole can produce invariant-violating
states.

% When people want to replicate data, they have to make a choice between strong and weak consistency. When choosing strong consistency, everything makes sense, reasoning is easy. But CAP and the latency one tell us that the avilability and latency of our system will be reduced. If we choose weak consistency, then things run really fast, but we can no longer reason about the application. In fact, we risk the possibility one our greatest tools that we use to reason about software: invariants. With weak consistency models , even if every transaction preserves the invariant, the invariant may still be broken when stuff is interleaved.

@@

% Is it possible to have our cake and eat it to? Can we maintain invariants without coordination? For some applications, yes. Invariant confluence (cite bailis) introduced a necessary and sufficient condition for when its possible to have coordination free replication while maintiang invariants. If somethign is iconfluent, it can be replicated wihtout coordination. However, determining whethere something is invariant-confluent is a very challening task. Bailis recognized some patterns of things which are invariant confluent, but ideally we would have a general purpose program to automatically determine it for us. The ultimate goal of this paper is to... In this paper, we make progress towards a more-general purpose iconfluence decision procedure, improving on the current state-of-the-art approaches.

@@

% This is hard. Not only undecidable, but also not really an easy thing to do. Existing systems often prove a sufficient condition called invariant-closure for invariant-confluence. So if the object is invariant-closed, they determine its invariant-confluent, but it its not invariant-closed, the system doesn't know anythign. In this paper, we study why the condition is not necessary, finding that the fundamental problem is that of unreachable invariant satisfying states. Using this insight, we develop general conditions under which invariant-closure is both necessary and sufficient.

@@

% Then, we use our insight to develop a general purpose interactive invariant-confluence decision procedure. Users continuously interact with the decision procedure to eleiminate unreachabel states from the invariant. Meanwhile, the decision procedure provides examples to the user that they can use to identify which points are reachable and which are not. This decision procedure can be used to show lots of things are invariant-confluent, and is also robust to user error.

% While the general purpose interaactive dp is good, it does rely on user input. We additionally invent a new sufficient condition for invariant-confluence known as merge-reducbility which exploits the insigths from the previous theory. This new sufficient condition can handle cases that invariant-closure cannot and doesn't require user feedback.

@@

% Finally, we address the elephant in the room and ask the question, what if something is not invariant-confluent though? We develop a generalization of invariant-confluence called segmented invariant-confluence. While invariant-confluence only characterizes objects which can be replicated without any coordination, segmented invariant-confluence allows us to replicate objects with minimal coordination. This approach also generalizes existing lock based approaches to handling non-invariant-confluent stuff.

% Finally, we implement all the decision procedures and the system models in a system called Lucy. We perform an evaluation to look at when the decision procedures are effective and measure the performance benefits of our implemetnation. Overall,

@@

% Hype up problem that invariant confluence solves
% Introduce iconfluence and hype it up as a really good thing.
% Discuss how it's hard to determine iconfluence and a lot of existing
% approaches fall short.
% Describe how we take the problem one step further
% Overview two new approaches
% Describe how often times we're not iconfluent
% Overivew new segmented iconfluence stuff
% contributions
%   - new expression-based definitions of iconfluence
%   - understanding of iclosure and new suff and necc
%   - interactive decision procedure
%   - new suff conditions
%   - segmented iconfluence
%   - implementation in lucy + evaluation...

>>>>

\section{Introduction}
When an application designer decides to replicate a piece of data, they have to
make a fundamental choice between weak and strong consistency. Replicating the
data with strong consistency using a technique like state machine
replication~\cite{schneider1990implementing, lamport1998part,
liskov2012viewstamped, ongaro2014search, moraru2013there, vincent2015designing,
oki1988viewstamped, lamport2005generalized, lamport2006fast} makes the
application designer's life very easy. To the application developer, a strongly
consistent system behaves exactly like a single-threaded system running on a
single node, so reasoning about the behavior of the system is
simple~\cite{herlihy1990linearizability}.  Unfortunately, strong consistency is
at odds with performance. The CAP theorem and PACELC theorem tell us that
strongly consistent systems suffer from higher latency at best and
unavailability at worst~\cite{gilbert2002brewer, brewer2012cap,
abadi2012consistency}. On the other hand, weak consistency models like
eventual consistency~\cite{vogels2009eventually}, PRAM consistency~\cite{lipton1988pram},
causal consistency~\cite{ahamad1995causal}, and others~\cite{lloyd2011don,
mehdi2017can} allow data to be replicated with high availability and low
latency, but they put a tremendous burden on the application designer to reason
about the complex interleavings of operations that are allowed by these weak
consistency models. In fact, weak consistency models strip an application
developer of one of the earliest and most effective tools that is used to
reason about the execution of programs: application
invariants~\cite{hoare1969axiomatic, balegas2015towards}. Even if every
transaction executing in a weakly consistent system individually maintains an
application invariant, the system as a whole can produce invariant-violating
states.

@@

@@

@@

@@

@@
